SeedLing: Building and using a seed corpus \\ for the Human Language Project

### 2014-05-19 docs/computEL-final/cluster.tex

\begin{table}[t]
\centering
    \begin{tabular}{l|ccc}
    ~        & Precision & Recall       & F-score    \\ \hline
	Base. 1: random	& 0.184	& 0.092	& 0.068 \\
	Base. 2: together	& 0.061	& 1.000	& 0.112 \\
	Base. 3: separate	& 1.000	& 0.086	& 0.122 \\ \hline
	SeedLing	& 0.255	& 0.205	& 0.150 
    \end{tabular}
\caption{Clustering compared with baselines}
\label{table:cluster}
\end{table}

@@

In Table \ref{table:cluster}, we set the number of clusters to be 105, the number of language families in our data, and compare this with three baselines: a random baseline (averaged over 20 runs); putting all languages in a single cluster; and putting all languages in separate clusters. Our clustering outperforms all baselines. It is worth noting that precision is higher than recall, which is perhaps expected, given that related languages using wildly differing orthographies will appear distinct.

@@

Interpreting the clusters directly is difficult, because they are noisy.  However, the distribution of cluster sizes mirrors the true distribution - for 105 clusters, we have 48 clusters of size 1 or 2, with the largest cluster of size 130; while in fact there are 51 families with only 1 or 2 languages in the data, with the largest of size 150.

>>>>

\begin{table}[t]
\centering
    \begin{tabular}{l|ccc}
    ~        & Precision & Recall       & F-score \\ \hline
	SeedLing	& 0.255	& 0.205	& 0.150 \\ \hline
	Base. 1: random	& 0.184	& 0.092	& 0.068 \\
	Base. 2: together	& 0.061	& 1.000	& 0.112 \\
	Base. 3: separate	& 1.000	& 0.086	& 0.122
    \end{tabular}
\caption{Clustering compared with baselines}
\label{table:cluster}
\end{table}

@@

In Table \ref{table:cluster}, we set the number of clusters to be 105, the number of language families in our data, and compare this with three baselines: a random baseline (averaged over 20 runs); putting all languages in a single cluster; and putting each language in a separate cluster. Our clustering outperforms all baselines. It is worth noting that precision is higher than recall, which is perhaps expected, given that related languages using wildly differing orthographies will appear distinct.

@@

Interpreting the clusters directly is difficult, because they are noisy.  However, the distribution of cluster sizes mirrors the true distribution - for 105 clusters, we have 48 clusters of size 1 or 2, with the largest cluster of size 130; while in our gold standard, there are 51 families with only 1 or 2 languages in the data, with the largest of size 150.

### 2014-05-19 docs/computEL-final/relwork.tex

Many of these archives are part of the Open Language Archive Community (OLAC), a subcommunity of the Open Archives Initiative.  OLAC maintains a metadata standard, based on the 15-element Dublin Core, which allows a user to search through all participating archives in a unified fashion.  However, centralising access to disparate resources, while of course extremely helpful, does not solve the problem of inconsistent standards.  Indeed, it can be difficult even to answer simple questions like ``how many languages are represented?''

>>>>

Many archives are part of the Open Language Archive Community (OLAC), a subcommunity of the Open Archives Initiative.  OLAC maintains a metadata standard, based on the 15-element Dublin Core, which allows a user to search through all participating archives in a unified fashion.  However, centralising access to disparate resources, while of course extremely helpful, does not solve the problem of inconsistent standards.  Indeed, it can even be hard to answer simple questions like ``how many languages are represented?''
